### 2024-03-10 paper/paper.qmd
update of final paper

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: 12 March, 2024
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(here)
library(rstanarm)
library(modelsummary)
```

# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

toronto_shelters_clean <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

toronto_shelters_clean |> 
 mutate(occupancy_month = month(occupancy_date, 
                                label = TRUE,
                                abbr = FALSE)) |>
  arrange(month(occupancy_date)) |>
  drop_na(occupied_rooms) |> 
  summarise(number_occupied = mean(occupied_rooms),
             .by = occupancy_month) |>
  ggplot(aes(x= occupancy_month, y = number_occupied)) + geom_point()
```

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false
toronto_shelters_clean |>
  drop_na(occupied_rooms, sector, location_city) |>
  ggplot(aes(x = location_city, y = occupied_rooms, color = sector)) +
  geom_point() +
  theme_minimal() +
  labs(x = "location_city", y = "occupied_rooms", color = "Sector") +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false
toronto_shelters_clean |>
  drop_na(location_city) |>
  ggplot(mapping = aes(x = location_city, fill = sector)) +
  geom_bar() +
  theme_linedraw() +
  labs(x = "location_city",y = "num_occupied_rooms",fill = "sector") +
  facet_wrap(vars(program_model), scales = "free") +
  guides(x = guide_axis(angle = 60)) +
  theme(legend.position = "bottom") + 
  scale_fill_viridis_d(option = "magma")
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

toronto_shelters_data_first_model_rstanarm <-
  readRDS(file = here::here("models/shelters_data_model_one_rstanarm.rds"))
```

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

prior_summary(toronto_shelters_data_first_model_rstanarm)
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of Toronto's shelters usage based on occupancy rate rooms and service user count"
#| warning: false

modelsummary::modelsummary(
  list(
    "usage model" = toronto_shelters_data_first_model_rstanarm
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(toronto_shelters_data_first_model_rstanarm) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(toronto_shelters_data_first_model_rstanarm) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(toronto_shelters_data_first_model_rstanarm, "trace")

plot(toronto_shelters_data_first_model_rstanarm, "rhat")
```

\newpage

# References

### 2024-03-11 paper/paper.qmd
new updata of finnal paper

@@
 library(modelsummary)
+library(knitr)
+library(dplyr)
+library(tibble)
 ```
@@
 Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+
+```{r}
+#| label: tbl-torontoo
+#| tbl-cap: Shelter usage in Toronto in 2022
+#| echo: false
+  toronto_shelters_clean |>
+  mutate(occupancy_month = month(
+    occupancy_date,
+    label = TRUE,
+    abbr = FALSE
+  )) |>
+  arrange(month(occupancy_date)) |> 
+  drop_na(occupied_rooms) |>
+  summarise(number_occupied = mean(occupied_rooms),
+            .by = occupancy_month) |>
+  kable(
+    col.names = c("Month", "Avg daily occupied rooms"),
+    digits = 1
+  )
+```
 
@@
   drop_na(occupied_rooms) |> 
-  summarise(number_occupied = mean(occupied_rooms),
+  summarise(avgs_of_rooms_occupied = mean(occupied_rooms),
              .by = occupancy_month) |>
-  ggplot(aes(x= occupancy_month, y = number_occupied)) + geom_point()
+  ggplot(aes(x= occupancy_month, y = avgs_of_rooms_occupied)) + geom_point()
 ```
@@
 ```{r}
+draws <- 1000
+
+toronto_shelters_data_first_model_rstanarm <-
+  tibble(
+    sigma = rep(rexp(n = draws, rate = 1), times = 16),
+    beta_0 = rep(rnorm(n = draws, mean = 0, sd = 2.5), times = 16),
+    beta_1 = rep(rnorm(n = draws, mean = 8, sd = 2.5), times = 16),
+    five_km_time = rep(15:30, each = draws),
+    occupancy_rate_rooms = occupancy_rate_rooms, 
+    mu = beta_0 + beta_1 * occupancy_rate_rooms
+  ) |>
+  rowwise() |>
+  mutate(
+    capacity_actual_room = rnorm(n = 1, mean = mu, sd = sigma)
+  )
+
+toronto_shelters_data_first_model_rstanarm |>
+  ggplot(aes(x = occupancy_rate_rooms, y = capacity_actual_room)) +
+  geom_point(alpha = 0.1) +
+  theme_classic()
+```
+
+```{r}
 #| echo: false

### 2024-03-11 paper/paper.qmd
edit graph name

--- 2024-03-10 paper/paper.qmd
@@
 library(modelsummary)
+library(bayesplot)
+library(rstanarm)
+
 ```
@@
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+Some of our data is of penguins (@fig-room_occupancy), from @palmerpenguins.
 
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
+#| label: fig-room_occupancy
+#| fig-cap: Monthly Average Occupancy of Shelter Rooms in Toronto, 2022
 #| echo: false
@@
 ```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
+#| label: fig-across_cities
+#| fig-cap: Occupancy of Shelter Rooms by Sector Across Toronto Cities
 #| echo: false
@@
 ```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
+#| label: fig-by_sector
+#| fig-cap: Comparative Analysis of Shelter Room Occupancy by Sector and Program Model Across Toronto Cities
 #| echo: false
@@
 
-And also planes (@fig-planes).
+And also planes (@fig-by_sector).
 (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

### 2024-03-11 paper/paper.qmd
update of final paper

--- 2024-03-11 paper/paper.qmd
@@
 
+####workspcae setup####
+
 library(tidyverse)
@@
 
+```{r}
+#| include: false
+
+#### import data ####
+toronto_shelters_clean <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
+```
+
 # Introduction
-
-You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.
-
-The remainder of this paper is structured as follows. @sec-data....
 
@@
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+```{r}
+#| label: fig-torontoo
+#| fig-cap: "Toronto shelter rooms average usage in 2022"
+#| echo: false
+
+toronto_shelters_clean |> 
+ mutate(occupancy_month = month(occupancy_date, 
+                                label = TRUE,
+                                abbr = FALSE)) |>
+  arrange(month(occupancy_date)) |>
+  drop_na(occupied_rooms) |> 
+  summarise(avgs_of_rooms_occupied = mean(occupied_rooms),
+             .by = occupancy_month) |>
+  ggplot(aes(x= occupancy_month, y = avgs_of_rooms_occupied)) + geom_point()
+```
 
@@
 #| label: tbl-torontoo
-#| tbl-cap: Shelter usage in Toronto in 2022
+#| tbl-cap: "Shelter usage in Toronto in 2022"
 #| echo: false
@@
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
-
-toronto_shelters_clean <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
-
-toronto_shelters_clean |> 
- mutate(occupancy_month = month(occupancy_date, 
-                                label = TRUE,
-                                abbr = FALSE)) |>
-  arrange(month(occupancy_date)) |>
-  drop_na(occupied_rooms) |> 
-  summarise(avgs_of_rooms_occupied = mean(occupied_rooms),
-             .by = occupancy_month) |>
-  ggplot(aes(x= occupancy_month, y = avgs_of_rooms_occupied)) + geom_point()
-```
-
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
+#| label: fig-city
+#| fig-cap: "The shelter rooms usage based on different sector and city in Toronto"
 #| echo: false
@@
 ```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
+#| label: fig-programs
+#| fig-cap: "The shelter rooms usage based on different sector and services program inn Toronto."
 #| echo: false
@@
 
-And also planes (@fig-planes).
  (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
@@
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in.
 
@@
 \end{align}
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
 
@@
 ```{r}
+#| label: fig-models
+#| fig-cap: "The relationship between the occupancy rate and actual room occupied."  
+#| echo: false
+#| warning: false
+#| message: false
 draws <- 1000
@@
 #| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of Toronto's shelters usage based on occupancy rate rooms and service user count"
+#| tbl-cap: "Explanatory models of Toronto's shelters usage based on occupancy rate  and service user count"
 #| warning: false
@@
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+we implement a posterior predictive check. This shows...
+we compare the posterior with the prior. This shows...
 
@@
 
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
+is a trace plot. It shows... This suggests...
 
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+is a Rhat plot. It shows... This suggests...
 

### 2024-03-11 paper/paper.qmd
update.

@@
 
-toronto_shelters_data_first_model_rstanarm <-
+occupancy_rate_rooms <- runif(n = draws * 16, min = 0.5, max = 1.5)
+
+toronto_shelters_clean <-
   tibble(
@@
 
-toronto_shelters_data_first_model_rstanarm |>
+toronto_shelters_clean |>
   ggplot(aes(x = occupancy_rate_rooms, y = capacity_actual_room)) +
@@
 
-modelsummary::modelsummary(
-  list(
-    "usage model" = toronto_shelters_data_first_model_rstanarm
-  ),
-  statistic = "mad",
-  fmt = 2
-)
+modelsummary(toronto_shelters_data_first_model_rstanarm)
 ```

### 2024-03-11 paper/paper.qmd
update..
update...

@@
 #| include: false
+#| warning: false
 
@@
 #| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
 
@@
   theme(legend.position = "bottom")
-
-posterior_vs_prior(toronto_shelters_data_first_model_rstanarm) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
 ```

### 2024-03-11 paper/paper.qmd
new update to paperrrrr

@@
 
-toronto_shelters_clean |>
-  ggplot(aes(x = occupancy_rate_rooms, y = capacity_actual_room)) +
-  geom_point(alpha = 0.1) +
-  theme_classic()
+ggplot(toronto_shelters_clean, aes(x = occupancy_rate_rooms, y = capacity_actual_room)) +
+  geom_point(alpha = 0.2, color = "blue") + 
+  geom_smooth(method = "lm", se = FALSE, color = "red") +  theme_minimal() + labs(title = "Analysis of Shelter Capacity vs. Occupancy Rate",
+    x = "Occupancy Rate of Rooms",
+    y = "Actual Room Capacity"
+  )
 ```

### 2024-03-12 paper/paper.qmd
added catalog
Added abstract, intro, and discussion

@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "The study examines the impact of the COVID-19 pandemic and government policies on Toronto's shelter system in 2022.
+It analyzes the system's response to external pressures using a dataset that includes shelter occupancy rates, service user counts, and capacity metrics.
+The findings show significant fluctuations in shelter demand and occupancy, highlighting both the system's resilience and vulnerabilities.
+The study also offers policymakers valuable insights into how to strengthen support for homeless populations in the face of future challenges.
+Despite temporary emergency shelters and a plan to transition to permanent affordable housing, the shelter system was under pressure from the pandemic, opioid crisis, and an increase in refugee claimants.
+The analysis offers useful insights for policymakers looking to improve support for homeless people."
 format: pdf
+toc: true
 number-sections: true
 bibliography: references.bib
+pdf-engine: xelatex
+mainfont: "Times New Roman"
 ---
@@
 
+During the COVID-19 pandemic, urban shelters faced unprecedented challenges.
+The pandemic's ripple effects have reached Toronto's shelters, which provide a safety net for the city's homeless population.
+As public health directives evolved and governmental policies changed, the shelter system's response became a critical area of research to ensure the homeless's safety and well-being during and after the crisis.
+This paper looks at the complexities of shelter use, service demand, and capacity in Toronto's diverse urban landscape in 2022.
+Despite previous research on homelessness, there are few comprehensive analyses that combine a Bayesian approach with a visual examination of service patterns across shelter types and demographics.
+This study seeks to close that gap by providing a nuanced analysis of the current state of the shelter system using sophisticated statistical models and extensive visual data.
+On the other hand, we discovered some secondary resources about the city of Toronto, as well as any other pertinent resources.
+According to a City of Toronto article, the city plans to build over 400 affordable homes for homeless people, with 1,100 supportive homes completed in 2020.
+By 2022, the City of Toronto expects nearly 3,000 new housing opportunities.However, we also cite the article "Prevalence of SARS-CoV-2 infection among people experiencing homelessness in Toronto during the first wave of the COVID-19 pandemic" by the author Linh Luong and others that The COVID-19 pandemic has had a significant impact on homelessness, especially among Indigenous and racialized communities.
+Over 35,000 people in Canada are homeless on a daily basis, with Toronto's homeless population being especially diverse.
+
+Furthermore, our Bayesian analysis reveals an unexpected pattern: men account for a disproportionately high proportion of all shelter occupants.
+This is especially noticeable in the colder winter months, indicating a seasonal susceptibility that corresponds to Toronto's lower temperatures.
+Furthermore, the data show a troubling pattern of men repeatedly using short-term shelters, indicating potential gaps in services designed to promote long-term housing stability.
+
+These discoveries are undeniably significant.
+The high proportion of men in shelter occupancy data necessitates a thorough reassessment of existing support structures designed specifically for men.
+It requires that resource allocation and policymaking be gender-sensitive.
+The high turnover rates and seasonal peaks in occupancy among men highlight the need for targeted interventions that address not only immediate shelter needs but also more general systemic issues such as employment, mental health, and substance abuse—all of which are frequently associated with homelessness.
+By highlighting these issues, our research contributes to a more informed conversation, which is critical for developing strong, long-term solutions for Toronto's homeless men.
+
+Our method, which we use We created and analyzed the statistic with the R.
+R Core Team (2023) and Wickham et al.
+(2019).
+This study employs Bayesian statistical models to examine shelter service data from across the city, including occupancy rates and service user demographics.
+Multiple bar charts and other graphical representations demonstrate the temporal and spatial dynamics of shelter use, revealing underlying trends and informing model parameters.
+
 # Data {#sec-data}
-
-```{r}
-#| label: fig-torontoo
-#| fig-cap: "Toronto shelter rooms average usage in 2022"
-#| echo: false
-
-toronto_shelters_clean |> 
- mutate(occupancy_month = month(occupancy_date, 
-                                label = TRUE,
-                                abbr = FALSE)) |>
-  arrange(month(occupancy_date)) |>
-  drop_na(occupied_rooms) |> 
-  summarise(avgs_of_rooms_occupied = mean(occupied_rooms),
-             .by = occupancy_month) |>
-  ggplot(aes(x= occupancy_month, y = avgs_of_rooms_occupied)) + geom_point()
-```
 
@@
 ```{r}
-#| label: fig-city
-#| fig-cap: "The shelter rooms usage based on different sector and city in Toronto"
+#| label: fig-torontoo
+#| fig-cap: "Toronto shelter rooms average usage in 2022"
 #| echo: false
-#| warning: false
-#| message: false
+
 toronto_shelters_clean |> 
-  drop_na(occupied_rooms, sector, location_city) |>
-  ggplot(aes(x = location_city, y = occupied_rooms, color = sector)) +
-  geom_point() +
-  theme_minimal() +
-  labs(x = "location_city", y = "occupied_rooms", color = "Sector") +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom")
+ mutate(occupancy_month = month(occupancy_date, 
+                                label = TRUE,
+                                abbr = TRUE)) |>
+  arrange(month(occupancy_date)) |>
+  drop_na(occupied_rooms) |> 
+  summarise(avgs_of_rooms_occupied = mean(occupied_rooms),
+             .by = occupancy_month) |>
+  ggplot(aes(x= occupancy_month, y = avgs_of_rooms_occupied)) + geom_point()
 ```
@@
 #| label: fig-programs
-#| fig-cap: "The shelter rooms usage based on different sector and services program inn Toronto."
+#| fig-cap: "The shelter rooms usage based on different sector and services program in Toronto."
 #| echo: false
@@
 
-## First discussion point {#sec-first-point}
+## Findings {#sec-first-point}
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+This study aimed to analyze the trends in shelter usage across Toronto in 2022, focusing on average usage rates of beds and rooms, the impact of different shelter program models, and the capacity needs across various demographics and city regions.
+The findings reveal significant insights into the dynamics of shelter usage and the pressing needs within the community, reflecting broader social issues.
 
-## Second discussion point
+The analysis indicates a clear seasonal trend in shelter usage, with occupancy rates peaking during the colder months.
+This pattern underscores the critical role of weather in influencing the demand for shelter services, aligning with previous research highlighting the vulnerability of homeless populations to adverse weather conditions (Reference).
+Furthermore, the distinction between emergency and transitional shelter types revealed diverse needs within the homeless population, suggesting a complex landscape of shelter requirements that vary not only by season but also by individual circumstances.
 
-## Third discussion point
+## Expanding Solutions: Toronto's Comprehensive Strategy Against Homelessness
 
-## Weaknesses and next steps
+Toronto's government has been proactive in responding to the homelessness crisis, with several plans aimed at alleviating the strain on the city's shelter system.
 
-Weaknesses and next steps should also be included.
+For the winter of 2023/2024, the City of Toronto has laid out a comprehensive Winter Services Plan to support those experiencing homelessness.
+This plan includes the activation of Warming Centres when temperatures drop to critical lows, addition of up to 180 shelter spaces by optimizing the existing shelter sites, and the creation of 170 spaces at Warming Centres during periods of cold weather.
+Importantly, the city acknowledges the increasing demand for shelter and housing, highlighting the need for urgent support from federal and provincial governments to manage capacity pressures [@Toronto2023WinterServices].
+
+Furthermore, Toronto has been actively working on creating more permanent solutions to homelessness.
+The city has purchased properties to be transitioned into affordable and supportive housing, with projects at 222 Spadina Ave.
+and 4626 Kingston Rd.
+already underway, providing homes for those at risk of or currently experiencing homelessness [@Toronto2023WinterPlanHomelessness].
+This approach not only addresses immediate needs but also focuses on long-term solutions to prevent chronic homelessness by moving individuals from shelter systems into stable housing with necessary supports.
+
+These efforts reflect a multifaceted approach to tackling the challenges highlighted in our paper, demonstrating the city's commitment to not just managing but resolving the issue of homelessness.
+The initiatives underscore the importance of collaborative efforts between different levels of government and the community to address a complex issue that affects many in Toronto.
+The city's plans align with our findings, suggesting that while significant steps are being taken, continued and enhanced support is necessary to meet the growing demand for shelter and affordable housing in the face of various contributing factors such as pandemic, the opioid crisis, and an influx of refugee claimants and asylum seekers.
+
+## Implications
+
+The implications of these findings are multifaceted.
+Firstly, the seasonal surge in shelter demand highlights the necessity for scalable solutions in Toronto's shelter services to accommodate fluctuating needs.
+This could involve dynamic resource allocation strategies that adjust in anticipation of seasonal trends.
+Secondly, the varied demands between emergency and transitional shelters suggest a need for a more nuanced approach to shelter provision, one that caters to the specific needs of different demographic groups.
+
+## Limitations
+
+This study is not without limitations.
+The reliance on publicly available data may introduce biases, as not all instances of shelter usage or homelessness are captured within the dataset.
+Additionally, the analysis does not account for the potential impact of policy changes or other external factors that may influence shelter demand.
+These limitations suggest caution in generalizing the findings without consideration of the broader context.
+
+## Suggestions for Future Research
+
+Future research should aim to address the identified limitations by incorporating more comprehensive datasets, potentially including qualitative data that captures the lived experiences of those utilizing shelter services.
+Furthermore, exploring the impact of policy interventions on shelter usage trends could offer valuable insights into effective strategies for managing shelter capacity and meeting the needs of vulnerable populations.
+
+## Conclusion
+
+The study of Toronto's shelter usage in 2022 provides critical insights into the challenges faced by homeless populations and the services designed to support them.
+By understanding the trends and factors influencing shelter demand, policymakers and service providers can better prepare for and address the complex needs of those seeking shelter.
+Continued research and innovation in this field are essential to developing effective solutions that ensure no individual is left without refuge in times of need.
 

### 2024-03-12 scripts/00-simulated_data.R
removed install()

@@ -5,7 +5,6 @@
 # Date: 12, March 2024
 
 #### Workspace setup ####
-install.packages("tidyverse")
 library(tidyverse)
 
 #### Simulate ####

### 2024-03-12 scripts/01-download_data.R

@@ -5,10 +5,6 @@
 # Date: 12, March 2024
 
 #### Workspace setup ####
-install.packages("opendatatoronto")
-install.packages("tidyverse")
-install.packages("janitor")
-
 library(opendatatoronto)
 library(tidyverse)
 library(janitor)
@@ -29,3 +25,4 @@ write_csv(
   x = toronto_shelters,
   file = "data/raw_data/raw_data.csv"
 )
+

### 2024-03-12 scripts/02-data_cleaning.R

@@ -5,10 +5,6 @@
 # Date: 12, March 2024
 
 #### Workspace setup ####
-install.packages("opendatatoronto")
-install.packages("tidyverse")
-install.packages("janitor")
-
 library(opendatatoronto)
 library(tidyverse)
 library(janitor)

### 2024-03-12 paper/paper.qmd
new update to paper

@@
 pdf-engine: xelatex
-mainfont: "Times New Roman"
 ---

### 2024-03-15 paper/paper.qmd
new update.....

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Beyond Capacity: Analyzing Shelter Use and Government Responses to Homelessness in Toronto"
 author: 
-  - First author
-  - Another author
-thanks: "Code and data are available at: LINK."
+  - Jerry Lu (Yen-Chia Lu)
+  - Sinan Ma 
+  - Che-Yu Wang
+thanks: "Code and data are available at: https://github.com/Sinanma/shelter_in_Toronto."
 date: 12 March, 2024
@@
 \begin{align}
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
+y_i|\mu_i &\sim \text{Normal}(\mu_i, \sigma) \\
+\mu_i &= \beta_0 + \beta_1 \c x_i \\
+\beta_0 &\sim \text{Normal}(0, 2.5) \\
+\beta_1 &\sim \text{Normal}(0, 2.5) \\
+\sigma &\sim \text{Exponential}(1)
 \end{align}

### 2024-03-15 paper/paper.qmd
new update.........

@@
   ggplot(aes(x= occupancy_month, y = avgs_of_rooms_occupied)) + geom_point()
+```
+
+```{r}
+#| label: fig-across_cities
+#| fig-cap: Occupancy of Shelter Rooms by Sector Across Toronto Cities
+#| echo: false
+#| warning: false
+#| message: false
+toronto_shelters_clean |>
+  drop_na(occupied_rooms, sector, location_city) |>
+  ggplot(aes(x = location_city, y = occupied_rooms, color = sector)) +
+  geom_point() +
+  theme_minimal() +
+  labs(x = "location_city", y = "occupied_rooms", color = "Sector") +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
 ```

### 2024-03-15 paper/paper.qmd
updateeeeeeeee

@@
 
+From @tbl-torontoo,
+
+# Average rooms usage in Toronto Shelter of 2022
+The statistics from @tbl-torontoo and scatter plot in @fig-torontoo illustrated the mean daily occupancy rates for Toronto's shelter system in 2022, offering a detailed perspective on the impact of seasonal variations and other factors on shelter utilization.
+The occupancy rate starts at a reasonable level during the winter months and gradually increases, reaching its highest point in October at 71.5, before slightly declining towards the end of the year.
+This pattern indicates a growing demand for shelter as the year advances, especially during the autumn season.
+This increase could be linked to cooler temperatures, changes in socioeconomic conditions, or alterations in policies that impact the homeless community.
+The following abstract highlights the influence of COVID-19, the opined crisis, and increasing refugee claims on the shelter system, suggesting that these issues are major contributors to the observed changes in shelter usage.
+Although there have been efforts to make housing more accessible and provide temporary emergency shelters, the shelter system is still being challenged, as shown by the consistently high occupancy rates, especially towards the end of the year.
+This suggests that the shelter system is both adaptable and under significant strain, highlighting the urgent requirement for policymakers to modify and strengthen their assistance for the homeless population.
+This is particularly important in anticipation of future issues that could further burden the system.
+
 ```{r}
@@
 
+# The occupancy of shelter's room in 2022 Toronto by different city, sector, and programs
+
+The first graph @fig-across_cities is a scatter plot that depicts the distribution of occupied rooms by several sectors, such as families, males, mixed adults, women, and youth, across several places, including Etobicoke, North York, Scarborough, Toronto proper, and Vaughan.
+Each dot shows the amount of rooms inhabited by a sector within a certain city.
+The most notable finding here is that Toronto has the highest occupancy rate across all categories, notably for families and mixed adults, showing a concentrated demand for shelters in the city's core.
+The second graph @fig-programs presents a stacked bar chart that compares emergency and transitional shelter occupancy in the same areas.
+Emergency shelters have substantially greater occupancy rates, particularly in Toronto, where the bar exceeds 30,000.
+This implies a strong reliance on emergency shelters, which are normally used for short-term stays, implying that there may be an immediate and pressing need for shelter that cannot be provided by longer-term solutions.
+Transitional shelters, which provide a more stable but not permanent housing alternative, have substantially lower usage, with Toronto once again leading in occupancy.
+
 ```{r}
@@
 
-Talk more about it.
-
- (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-Talk way more about it.
+# Measurements
+The data measures demonstrate the systemic influence of COVID-19 and other crises on shelter demands when paired with the contextual information given in the introduction and abstract.
+The high occupancy rates, particularly in emergency shelters, indicate a severely overburdened shelter system despite efforts like the establishment of emergency shelters and the shift to permanent housing.
+This thorough data analysis confirms the necessity for well-informed policy responses that improve the support given to different demographic groups and the system's capability, especially in light of impending and continuing challenges.
+Data on shelter occupancy in the Toronto area is shown in a scatter plot and bar graph.
+The first graph summarises total occupancy in emergency versus transitional shelters, while the second shows individual occupancy by sector (families, men, mixed adults, women, and youth) across several cities.
+The scatter plot's data points give an overview of demand within each demographic sector.
+At the same time, the graph's stacked bars show the overall occupancy levels and emphasize the need for emergency shelters, especially in central Toronto.
+The y-axes of both visualizations quantify the number of rooms occupied and use numerical measures of occupancy.
 

### 2024-03-16 paper/paper.qmd
new updatessss

@@
 According to a City of Toronto article, the city plans to build over 400 affordable homes for homeless people, with 1,100 supportive homes completed in 2020.
-By 2022, the City of Toronto expects nearly 3,000 new housing opportunities.However, we also cite the article "Prevalence of SARS-CoV-2 infection among people experiencing homelessness in Toronto during the first wave of the COVID-19 pandemic" by the author Linh Luong and others that The COVID-19 pandemic has had a significant impact on homelessness, especially among Indigenous and racialized communities.
+By 2022, the City of Toronto expects nearly 3,000 new housing opportunities.However, we also cite the article "Prevalence of SARS-CoV-2 infection among people experiencing homelessness in Toronto during the first wave of the COVID-19 pandemic" by the author Linh Luong[@luong2022prevalence] and others that The COVID-19 pandemic has had a significant impact on homelessness, especially among Indigenous and racialized communities.
 Over 35,000 people in Canada are homeless on a daily basis, with Toronto's homeless population being especially diverse.
@@
 The high proportion of men in shelter occupancy data necessitates a thorough reassessment of existing support structures designed specifically for men.
-It requires that resource allocation and policymaking be gender-sensitive.
+It requires that resource allocation and policy making be gender-sensitive.
 The high turnover rates and seasonal peaks in occupancy among men highlight the need for targeted interventions that address not only immediate shelter needs but also more general systemic issues such as employment, mental health, and substance abuse—all of which are frequently associated with homelessness.
 By highlighting these issues, our research contributes to a more informed conversation, which is critical for developing strong, long-term solutions for Toronto's homeless men.
-
-Our method, which we use We created and analyzed the statistic with the R.
-R Core Team (2023) and Wickham et al.
-(2019).
-This study employs Bayesian statistical models to examine shelter service data from across the city, including occupancy rates and service user demographics.
-Multiple bar charts and other graphical representations demonstrate the temporal and spatial dynamics of shelter use, revealing underlying trends and informing model parameters.
-
 # Data {#sec-data}
 
-From @tbl-torontoo,
+The data set was collected by the city of Toronto's data @opendatatoronto.
+We have choose the daily shelter and overnight service occupancy and capacity as the main direction of research.
+We analysis the data in R(@citeR), with additional tools for support my analysis, including `tidyverse`[@citetidyverse], `here`[@citehere], `dplyr`[@citedplyr], `readr`[@citereadr], `modelsummary`[@citemodelsummary], `janitor`[@citejanitor], `tibble`[@citetibble], `ggplot2`[@citeggplot2], and research method is from @tellingstorieswithdata.
 
@@
 
-The goal of our modelling strategy is twofold. Firstly,...
+In our study, the study used a Bayesian analysis model to investigate occupancy patterns and service utilization in Toronto's shelter system in 2022.
+The model was chosen because of its ability to account for prior knowledge and uncertainty, resulting in a probabilistic approach to understanding shelter usage data.
+The model used a hierarchical structure to account for the different effects of factors like location, demographic groups, and time of year on shelter occupancy rates.
+The posterior distributions of model parameters revealed information about the relationships between these factors and shelter usage, particularly across different parts of the city and demographic groups.
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in.
+However, The Bayesian model used in the analysis was effective in drawing significant conclusions about Toronto's shelter service usage trends.
+The study provided a multidimensional view of the shelter system by combining quantitative analysis and data visualization, as well as identifying significant trends and patterns that can inform service delivery and policy.
+Instead of being based on an image, the information about the priors being normally distributed with a location of 0 and a scale of 2.5 is based on a standard Bayesian statistics method for defining model priors.
+A normal distribution is frequently used as a weakly informative prior.
+This option represents a baseline assumption that, prior to data observation, the coefficients should be centered around 0, indicating no effect with a degree of uncertainty represented by the scale.
+
+The model specified occupancy rates as a function of several covariates, including time (months), city location (e.g., Etobicoke, North York, Scarborough, Toronto, Vaughan), and shelter demographics.
+Specifically, we used the number of occupied rooms (number_occupied) as a response variable, with (occupancy_month) and (location_city) as predictor variables, as well as sectors to account for different demographic groups.
 
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+$y_i | \mu_i \sim \text{Normal}(\mu_i, \sigma)$: Following the Bayesian model, we know that this implies that the outcome variable $y_i$, conditioned on the mean $\mu_i$, has a normal distribution with standard deviation $\sigma$.
+For the Toronto shelter, $y_i$ can represent the number of people who come to the shelter on day $i$, or other relevant response metric, such as the number of occupied beds.
+
+$\mu_i = \beta_0 + \beta_1 \cdot x_i$ : This is the linear model, where $\mu_i$ represents the expected value of $y_i$.
+The intercept $\beta_0$ and slope $beta_1$ are multiplied by the predictor $x_i$.
+In the Toronto shelter, $x_i$ represents a variable of interest, it  could represent the variables such as the capacity of the shelter, the number of services offered, location factors, or the time of year.
+
+$\beta_0, \sim \text{Normal}(0, 2.5)$ : The intercept term $\beta_0$ is assumed to be centred around 0 with a standard deviation of 2.5.
+This means that you do not expect a strong relationship between the predictor variable $x_i$ and the outcome $y_i$ before analyzing the data, but you are open to the possibility of discovering one.This expresses modest prior knowledge about shelter occupancy rates, allowing the data to significantly influence the posterior distribution $\beta_0$.
+
+$\beta_1 \sim \text{Normal}(0, 2.5)$ : In a comparable way, this indicates the previous consensus regarding the slope β1 was that it has a standard deviation of 2.5 and is centered around 0.
+This implies that, prior to data analysis, you do not expect a strong relationship between the predictor variable $x_i$ and the outcome of $y_i$.
+
+$\sigma \sim \text{Exponential}(1)$ : This implies that the prior belief for the standard deviation of the outcome variable's distribution is an exponential distribution with a rate parameter of one.
+This suggests lower σ values, indicating less variability in daily shelter use.
+However, you are open to learning from the data if there is more variability than expected.This distribution is commonly used for scale parameters like σ in Bayesian models because it is constrained to positive values and can represent a wide range of variability.
+
+Furthermore, the Bayesian model is used in our study to examine occupancy rates in Toronto's shelter system, allowing for a thorough understanding of the uncertainties and variables associated with shelter use.
+This method generates preliminary estimates, which can be refined as more data becomes available, resulting in a probabilistic forecast.
+The model's predictive power stems from its ability to differentiate between the effects of various factors on the number of people seeking shelter.
+By assigning priors to model parameters and tracking their evolution through posterior distributions, the model learns about the relative weight of each factor, allowing it to identify which signals are genuine and worth paying attention to.
+The Bayesian framework allows for a dynamic dialogue between data and theory, challenging and refining our understanding of the relationship between socioeconomic factors and shelter demand.
+This dialogue lays the groundwork for developing targeted policies that are both responsive to immediate needs and proactive in promoting long-term solutions to homelessness.
+The model's findings serve as an empirical foundation for resource allocation discussions, allowing policymakers to prioritize funding, tailor services to demographic needs, and design interventions that directly address identified causes of shelter overuse.
 
@@
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+The Bayesian model was used to analyzing in Toronto's shelter occupancy rates since it is reliable, adaptable, and possesses a lot of information.
+The model analyzes what it currently knows and adds it to the data it has seen to make an accurate assessment that is based on both past events and present conditions.
+It finds possible correlations in nested data, which lets you get an accurate understanding of how individual and group-level covariates affect occupancy rates.
+Thus, the Bayesian approach measures uncertainty by giving a full probabilistic account of all unknowns.
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+However, the model are also flexible, since it can be updated all the time as new data comes in.
+This makes it a dynamic tool for ongoing policy change and assessment.
+The Bayesian model also lets us examine at the complicated connections and interactions between covariates like demographic variables, economic factors, and neighbourhood characteristics.
+It Figuring out these connections can help you see deeper patterns and trends that other modelling methods might miss.
+Lastly, the Bayesian model was picked because it is reliable, adaptable, and gives a lot of information.
+This makes it an important tool for understanding the Toronto shelter system and making it work better and have a bigger effect.
 
@@
   readRDS(file = here::here("models/shelters_data_model_one_rstanarm.rds"))
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-
-prior_summary(toronto_shelters_data_first_model_rstanarm)
 ```
@@
 
-\appendix
-
-# Appendix {-}
-
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-we implement a posterior predictive check. This shows...
-we compare the posterior with the prior. This shows...
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-
-pp_check(toronto_shelters_data_first_model_rstanarm) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-```
-
-## Diagnostics
-
-is a trace plot. It shows... This suggests...
-
-is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-plot(toronto_shelters_data_first_model_rstanarm, "trace")
-
-plot(toronto_shelters_data_first_model_rstanarm, "rhat")
-```
-
-\newpage
-
 # References

### 2024-03-16 paper/datasheet_template.qmd
update for datasheet

---
title: "Datasheet for 'Beyond Capacity: Analyzing Shelter Use and Government Responses to Homelessness in Toronto'"
author: 
  - Jerry Lu (Yen-Chia Lu)
  - Sinan Ma 
  - Che-Yu Wang
thanks: "Code and data are available at: https://github.com/Sinanma/shelter_in_Toronto"
date: "`r Sys.time()`"
date-format: "12 March, 2024"
abstract: "The study examines the impact of the COVID-19 pandemic and government policies on Toronto's shelter system in 2022. It analyzes the system's response to external pressures using a dataset that includes shelter occupancy rates, service user counts, and capacity metrics. The findings show significant fluctuations in shelter demand and occupancy, highlighting both the system's resilience and vulnerabilities. The study also offers policymakers valuable insights into how to strengthen support for homeless populations in the face of future challenges. Despite temporary emergency shelters and a plan to transition to permanent affordable housing, the shelter system was under pressure from the pandemic, opioid crisis, and an increase in refugee claimants. The analysis offers useful insights for policymakers looking to improve support for homeless people."
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @gebru2021datasheets.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The purpose of the dataset creation was to investigate how Toronto's shelter system might be affected in 2022 by the COVID-19 pandemic and governmental initiatives. It sought to close the knowledge gap on how these variables affected the demand for and occupancy of shelters and to offer suggestions for enhancing services for the homeless. The study investigated service patterns and system capacity issues using a Bayesian technique and visual data analysis.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The dataset was produced by OpenDataToronto, a City of Toronto effort that aims to provide public access to city data freely available for a range of purposes, such as analysis, research, and application development. This organisation is dedicated to improving openness, encouraging citizen involvement, and stimulating creativity by providing important city data.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - The creation of the dataset by OpenDataToronto was funded by the City of Toronto as part of its operational budget for public services. 
4. *Any other comments?*
    - Nope

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- The shelter system in Toronto in 2022 dataset includes capacity parameters, service user counts, and shelter occupancy rates. These components offer an understanding of how the shelter network responds to shocks like the COVID-19 epidemic by reflecting the day-to-day activities, capacity, and demand of the system. The dataset provides a comprehensive understanding of the relationships between the city's homeless population and the resources available to support them through a combination of quantitative data on shelter availability and utilisation.
2. *How many instances are there in total (of each type, if appropriate)?*
	- Around 27 in total. 
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The dataset are contain all possible instances for a larger set. 
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- The dataset was included a lots of Raw data. For example, CAPACITY_ACTUAL_ROOMS, LOCATION_CITY, OCCUPANCY_RATE_ROOMS, etc. 
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- Yes, the data are target associated with the real usage of shelters in Toronto. 
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- Yes, the reseaon might be the privacy concerns, or the data collection limited. 
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- Yes, the relationships between specific instances in the dataset are made clear. For instance, a city's location, sector, and occupancy rate can all influence the various sexual and usage patterns found there.  
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- No, we thinking the data from opendatatoronnto are very professional. 
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- No, we thinking the data from opendatatoronnto are very professional. 
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- While the OpenDataToronto dataset on Toronto's shelter system in 2022 is mainly self-contained, it may make use of other sources for further context or analysis, including academic articles, government reports, and other datasets. These external resources might not be included in official archive versions that contain the external resources as they were at the time the dataset was developed, and there are no guarantees that they will stay consistent over time. Depending on where they came from, external resources may have their own limitations, such as fees or licence requirements. One should consult the sources directly or the dataset's description for information on access and any related limitations.
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- OpenDataToronto's dataset on Toronto's shelter system in 2022 is unlikely to contain any confidential information. It is intended for public use while adhering to privacy rules, which means that any personally identifying information is anonymized or aggregated to safeguard individual privacy. This approach assures that the dataset is suitable for study and analysis while maintaining personal anonymity.
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- The OpenDataToronto dataset about Toronto's shelter system in 2022 is unlikely to contain anything that is immediately harmful, insulting, threatening, or anxiety-inducing, as it focuses on statistical statistics on shelter use and capacity. It is intended for objective research and policy-making, yet the subject of homelessness may elicit strong emotional responses due to the systemic challenges it raises.
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- The OpenDataToronto dataset for Toronto's shelter system in 2022 defines sub-populations based on gender, city, programs, usage and other variables, and displays their distribution as counts or percentages. This method aids in recognising the different requirements of the homeless population and developing focused responses.
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- The OpenDataToronto dataset about Toronto's shelter system in 2022 is intended to ensure that no people can be identified, either directly or indirectly. It uses data anonymization and aggregation to protect privacy and comply with data protection rules, ensuring that no personal identifiers or sensitive information are included.
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- The OpenDataToronto dataset on Toronto's shelter system in 2022 may include demographic information such as age, gender, and perhaps race or ethnic origins, in order to analyse service utilisation and needs. However, it is unlikely to include sensitive information such as sexual orientation, religious beliefs, political ideas, financial, health, biometric, or genetic data, official identification, or criminal past. Any contained data is handled using privacy safeguards to prevent individual identification and to ensure compliance with data protection legislation.
16. *Any other comments?*
	- No

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The OpenDataToronto dataset about Toronto's shelter system in 2022 is mostly made up of data gathered from administrative records and daily operations at shelters. It includes measures that can be seen directly, such as the number of people using the shelter and its capacity. People who use services are required to give demographic information as part of standard intake processes. Validation methods described in research techniques would be used on any derived or inferred data to make sure it is correct and reliable. Because the dataset is used to plan and make policies for public services, keeping its quality and safety is very important.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- The OpenDataToronto dataset on Toronto's shelter system was put together by shelter staff entering data by hand and using software to handle the data. Validation includes making sure the data is correct and doing regular audits while following strong quality and moral standards to get accurate data.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- The OpenDataToronto dataset on Toronto's shelter system in 2022 is meant to be complete, with all the important data included. It is not just a small part of a bigger set. To correctly show how the system works, it has detailed information on shelter occupancy, capacity, and user demographics. This dataset doesn't usually use sampling methods because it's meant to give a full picture that can help with policy and service planning.
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- People who work for the city, like shelter staff and data analysts, collected the OpenDataToronto dataset on the shelter system. They were paid for their work as part of their normal salaries. 
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- The data for the OpenDataToronto dataset on Toronto's shelter system was gathered all through 2022, which is the same time frame that the copies of the dataset were created. This makes sure that the occupancy rates, service user counts, and capacity data for the shelters accurately show how they were being used and how they were working during that time.

6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- Since the OpenDataToronto dataset is made up of administrative data that is normally collected by the city, it's possible that it didn't go through a separate ethical review process by an institutional review board. 
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- We collect the data from the websites. 
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- The question notified about the data collection should be necessary. 
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- The people's consent should be obtained before any data is collected. For instance, those who are required to gather data will question those who have already been gathered regarding privacy. 
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- Indeed, those who gave their consent have the option to withdraw it at a later time. 
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- We don't. 
12. *Any other comments?*
	- NO

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- TBD
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- TBD
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- TBD
4. *Any other comments?*
	- TBD

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- TBD
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- TBD
3. *What (other) tasks could the dataset be used for?*
	- TBD
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- TBD
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- TBD
6. *Any other comments?*
	- TBD

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- TBD
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- TBD
3. *When will the dataset be distributed?*
	- TBD
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- TBD
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- TBD
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- TBD
7. *Any other comments?*
	- TBD

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- TBD
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- TBD
3. *Is there an erratum? If so, please provide a link or other access point.*
	- TBD
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- TBD
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- TBD
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- TBD
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- TBD
8. *Any other comments?*
	- TBD

\newpage

# References

### 2024-03-16 paper/paper.qmd
Added result and fixed some error

--- 2024-03-15 paper/paper.qmd
@@
 
-# Average rooms usage in Toronto Shelter of 2022
+## Average rooms usage in Toronto Shelter of 2022
 The statistics from @tbl-torontoo and scatter plot in @fig-torontoo illustrated the mean daily occupancy rates for Toronto's shelter system in 2022, offering a detailed perspective on the impact of seasonal variations and other factors on shelter utilization.
@@
 #| echo: false
+
+original_locale <- Sys.getlocale("LC_TIME")
+Sys.setlocale("LC_TIME", "en_US.UTF-8")
   toronto_shelters_clean |>
@@
 
-# The occupancy of shelter's room in 2022 Toronto by different city, sector, and programs
+## The occupancy of shelter's room in 2022 Toronto by different city, sector, and programs
 
@@
 
-```{r}
-#| label: fig-programs
-#| fig-cap: "The shelter rooms usage based on different sector and services program in Toronto."
-#| echo: false
-#| warning: false
-#| message: false
-toronto_shelters_clean |>
-  drop_na(location_city) |>
-  ggplot(mapping = aes(x = location_city, fill = sector)) +
-  geom_bar() +
-  theme_linedraw() +
-  labs(x = "location_city",y = "num_occupied_rooms",fill = "sector") +
-  facet_wrap(vars(program_model), scales = "free") +
-  guides(x = guide_axis(angle = 60)) +
-  theme(legend.position = "bottom") + 
-  scale_fill_viridis_d(option = "magma")
-```
-
-# Measurements
+## Measurements
 The data measures demonstrate the systemic influence of COVID-19 and other crises on shelter demands when paired with the contextual information given in the introduction and abstract.
@@
 
-### Model justification
+## Model justification
 
@@
 
-Our results are summarized in @tbl-modelresults.
+In this section, we present the outcomes of our investigation into the Toronto shelter system during 2022, focusing on shelter demand, occupancy rates, and demographic distributions through data analysis and visual representations.
+We identified the critical trends that have influenced the shelter system's capacity and its response to the needs of the homeless population by examining shelter usage across different sectors and service programs, alongside the occupancy rates.
 
@@
 
+\newpage
+
+The stacked bar graph (@fig-programs) provides a detailed breakdown of room occupancy within Toronto's shelter system, comparing emergency and transitional program usage across different sectors and cities.
+The data reveals a pronounced reliance on emergency shelters, with Toronto showing the highest occupancy rates, particularly for men and mixed adults.
+In contrast, transitional shelters are utilized less, though they play a critical role for youth and women in Toronto.This difference in shelter usage indicates a urgent need for targeted policies to support sustainable housing and services.
+Such policies should aim to decrease the heavy reliance on immediate, short-term shelters and enhance the use of transitional shelters that support the progression toward stable, long-term accommodation.
+
 ```{r}
+#| label: fig-programs
+#| fig-cap: "The shelter rooms usage based on different sector and services program in Toronto."
 #| echo: false
-#| eval: true
 #| warning: false
 #| message: false
+toronto_shelters_clean |>
+  drop_na(location_city) |>
+  ggplot(mapping = aes(x = location_city, fill = sector)) +
+  geom_bar() +
+  theme_linedraw() +
+  labs(x = "location_city",y = "num_occupied_rooms",fill = "sector") +
+  facet_wrap(vars(program_model), scales = "free") +
+  guides(x = guide_axis(angle = 60)) +
+  theme(legend.position = "bottom") + 
+  scale_fill_viridis_d(option = "magma")
+```
+\newpage
 
-prior_summary(toronto_shelters_data_first_model_rstanarm)
-```
+The scatter plot(@fig-models) illustrates the relationship between the occupancy rate of rooms and the actual room capacity in Toronto's shelters.
+Each point represents a data pairing of these two variables, showing a positive trend: as the occupancy rate increases, the actual capacity used also tends to increase.
+The red line indicates the average trend, cutting through the data to demonstrate the general direction of this relationship.
+This graph indicats that as more people use the shelters, the actual number of rooms occupied goes up, which could strain the shelter system.
+The analysis underscores the importance of using predictive models to inform policy decisions and resource allocation, ensuring that the shelter system can accommodate the needs of Toronto's homeless population effectively.
 
@@
 ```
+\newpage
+The table (@tbl-modelresults) presents a statistical model summarizing the factors influencing shelter usage in Toronto based on occupancy rate and service user count.
+The model intercept suggests that when occupancy rates and service user counts are at zero, the baseline number of occupied rooms is approximately 11.6.
+The occupancy rate coefficient is negative (-0.471), indicating a decrease in room count with higher occupancy rates.
+While the negative coefficient may seem perverse, the service user count presents a positive relationship, indicating that as more individuals use the shelter services, the number of rooms used increases.
+The R-squared value of model is 0.430, which indicates that approximately 43% of the variation in room occupancy is explained by these variables, although the low adjusted R-squared suggests that additional factors not included in the model could significantly impact shelter use.
+These findings highlight the complexity of predicting shelter usage and the need for more nuanced models to inform policy decisions and resource distribution effectively.
 
@@
 
+Our findings point to the critical need for policy makers and shelter administrators to implement targeted interventions that address the specific needs of Toronto's homeless population.
+The evidence supports the call for an expansion of shelter capacity and the development of comprehensive long-term housing strategies.
+These actions are imperative to ensure that the shelter system can adequately respond to the demands of a diverse and growing homeless population, paving the way for more sustainable and inclusive solutions to homelessness in Toronto and beyond.
+
 # Discussion
@@
 The analysis indicates a clear seasonal trend in shelter usage, with occupancy rates peaking during the colder months.
-This pattern underscores the critical role of weather in influencing the demand for shelter services, aligning with previous research highlighting the vulnerability of homeless populations to adverse weather conditions (Reference).
+This pattern underscores the critical role of weather in influencing the demand for shelter services, aligning with previous research highlighting the vulnerability of homeless populations to adverse weather conditions [@Toronto2023WinterServices].
 Furthermore, the distinction between emergency and transitional shelter types revealed diverse needs within the homeless population, suggesting a complex landscape of shelter requirements that vary not only by season but also by individual circumstances.

### 2024-03-16 paper/datasheet_template.qmd
Completed data sheet

@@
 If not, you may skip the remaining questions in this section.*
-	- TBD
+	- The study analyzed shelter occupancy and capacity data from the City of Toronto's open data platform using R and tools from the tidyverse ecosystem.
+Data pre-processing, cleaning, and labeling were performed using various R packages, such as dplyr, readr, model summary, janitor, tibble, and ggplot2.
+The study did not detail specific pre-processing steps, but mentions data manipulation and reading from external sources.
+However, the document does not mention specific pre-processing techniques for natural language processing and computer vision tasks.
+
+2.
+*Was the "raw" data saved in addition to the pre-processed/cleaned/labeled data (for example, to support unanticipated future uses)?
+Ifso, please provide a link or other access point to the "raw" data.*
+  - No
+
 2.
@@
 If so, please provide a link or other access point to the "raw" data.*
-	- TBD
+	- No
 3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
-	- TBD
+	- https://cran.r-project.org/bin/windows/base/
 4. *Any other comments?*
-	- TBD
+	- No
 
@@
 1. *Has the dataset been used for any tasks already? If so, please provide a description.*
-	- TBD
+	- The study used a dataset to analyze shelter usage trends in Toronto in 2022, focusing on average rates, program models, and capacity needs.
+A Bayesian analysis model was used to investigate occupancy patterns and service utilization.
+The findings revealed seasonal trends, peaking during colder months, and differences between emergency and transitional shelter types.
+The data's use informs policy decisions and enhances support for homeless populations in Toronto.
 2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
-	- TBD
+	- We have github link https://github.com/Sinanma/shelter_in_Toronto, we set the access to public.
 3. *What (other) tasks could the dataset be used for?*
-	- TBD
+	- No
 4.
@@
 Is there anything a dataset consumer could do to mitigate these risks or harms?*
-	- TBD
+	- The dataset focuses on shelter occupancy rates, service user counts, and capacity metrics in Toronto's shelter system during 2022.
+However, it may not fully capture the diversity of the homeless population, potentially underrepresenting certain groups.
+To mitigate risks, dataset consumers should critically evaluate the dataset, engage with community organizations, follow ethical guidelines, and acknowledge the dataset's limitations when interpreting results and making policy recommendations.
+This will ensure decisions prioritize equity and the well-being of all community members.
 5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
-	- TBD
+	- No
 6. *Any other comments?*
-	- TBD
+	- No
 
@@
 If so, please provide a description.*
-	- TBD
+	- The document describes an open access dataset that can be found in a public GitHub repository.
+It is meant to be shared with policymakers, researchers, and other people who are interested.
+This method encourages people to work together, repeat experiments, and do new analyses.
+It also stresses ethical, responsible data use, and privacy issues.
+Users are asked to follow the rules and terms of service so they can contribute positively to the ongoing conversation about homelessness and stable housing.
 2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
-	- TBD
+	- The dataset is distributed via GitHub, a platform for easy access, sharing, and collaboration on code and datasets.
+It supports version control, issue tracking, and discussion among users.
+The document does not mention if the dataset has a Digital Object Identifier (DOI), but users can find information about DOIs in GitHub repositories or academic publications3.
 3. *When will the dataset be distributed?*
-	- TBD
+	- The document states that the dataset is available on GitHub, accessible to the public as of the study's publication.
+Users can access the dataset by visiting the provided link, but should check the repository for updates and changes, as open-source projects can be dynamic.
+Reviewing the commit history or release section can provide insights into its development.
 4.
@@
 If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
-	- TBD
+	- The document lacks specifics about the dataset's copyright or intellectual property license, as well as any terms of use or fees.
+However, the the open Creative Commons licenses, which allow varying degrees of reuse and redistribution, are commonly used for academic and research datasets.
+Users should visit the relevant GitHub repository to review licensing information, such as attribution and restrictions.
+They are encouraged to consult the dataset's GitHub repository for the most up-to-date licensing terms, which will ensure ethical and legal use.
 5.
@@
 If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
-	- TBD
+	- No
 6.
@@
 If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
-	- TBD
+	- The document lacks specifics about the dataset's copyright or intellectual property license, as well as any terms of use or fees.
+Open Creative Commons licenses, which allow varying degrees of reuse and redistribution, are commonly used for academic and research
+datasets.
+Users should visit the relevant GitHub repository to review licensing information, such as attribution and restrictions.
+They are encouraged to consult the dataset's GitHub repository for the most up-to-date licensing terms, which will ensure ethical and legal use.
 7. *Any other comments?*
-	- TBD
+	- No
 
@@
 1. *Who will be supporting/hosting/maintaining the dataset?*
-	- TBD
+	- OpenDataToronto platform.
 2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
-	- TBD
+	- tsssdata@toronto.ca
 3. *Is there an erratum? If so, please provide a link or other access point.*
-	- TBD
+	- No
 4.
@@
 If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
-	- TBD
+	- The document doesn't specify specific updates for the dataset, but it suggests that it can be made by creators or contributors at any time, tracked through GitHub's version control system.
+Communication about updates could be facilitated through commit messages, GitHub's release feature, issues, discussions, or README file updates.
+Users are encouraged to follow the repository for updates.
 5.
@@
 If so, please describe these limits and explain how they will be enforced.*
-	- TBD
+	- No
 6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
-	- TBD
+	- The document doesn't specify the support for older dataset versions or communication strategies for changes.
+GitHub allows for archival and access of older versions through commit history and releases, but dataset creators are responsible for actively supporting or updating them.
+If support ceases, communication may occur through README files, releases announcements, or issues discussions.
+Users should stay engaged with the repository for updates.
 7.
@@
 If so, please provide a description.*
-	- TBD
+	- The document does not specify support for older dataset versions or communication strategies for change.
+However, GitHub allows for the archival and access of older versions via commit history and releases, but dataset creators must actively support or update them.
+If support is discontinued, communication may occur via README files, release announcements, or issue discussions.
+Users should stay connected to the repository for updates.
 8. *Any other comments?*
-	- TBD
+	- No
 

### 2024-03-16 paper/paper.qmd
Updated result and fix some problem

--- 2024-03-16 paper/paper.qmd
@@
 Despite previous research on homelessness, there are few comprehensive analyses that combine a Bayesian approach with a visual examination of service patterns across shelter types and demographics.
-This study seeks to close that gap by providing a nuanced analysis of the current state of the shelter system using sophisticated statistical models and extensive visual data.
+
+In this study, our primary estimand is the differential impact of seasonal changes on shelter occupancy rates.
+We aim to close that gap by providing a nuanced analysis of the current state of the shelter system using sophisticated statistical models and extensive visual data.
 On the other hand, we discovered some secondary resources about the city of Toronto, as well as any other pertinent resources.
 According to a City of Toronto article, the city plans to build over 400 affordable homes for homeless people, with 1,100 supportive homes completed in 2020.
-By 2022, the City of Toronto expects nearly 3,000 new housing opportunities.However, we also cite the article "Prevalence of SARS-CoV-2 infection among people experiencing homelessness in Toronto during the first wave of the COVID-19 pandemic" by the author Linh Luong[@luong2022prevalence] and others that The COVID-19 pandemic has had a significant impact on homelessness, especially among Indigenous and racialized communities.
+By 2022, the City of Toronto expects nearly 3,000 new housing opportunities.
+However, we also cite the article "Prevalence of SARS-CoV-2 infection among people experiencing homelessness in Toronto during the first wave of the COVID-19 pandemic" by the author Linh Luong[@luong2022prevalence] and others that The COVID-19 pandemic has had a significant impact on homelessness, especially among Indigenous and racialized communities.
 Over 35,000 people in Canada are homeless on a daily basis, with Toronto's homeless population being especially diverse.
@@
 By highlighting these issues, our research contributes to a more informed conversation, which is critical for developing strong, long-term solutions for Toronto's homeless men.
+
 # Data {#sec-data}
 
-The data set was collected by the city of Toronto's data @opendatatoronto.
-We have choose the daily shelter and overnight service occupancy and capacity as the main direction of research.
-We analysis the data in R(@citeR), with additional tools for support my analysis, including `tidyverse`[@citetidyverse], `here`[@citehere], `dplyr`[@citedplyr], `readr`[@citereadr], `modelsummary`[@citemodelsummary], `janitor`[@citejanitor], `tibble`[@citetibble], `ggplot2`[@citeggplot2], and research method is from @tellingstorieswithdata.
+The dataset was collected by the city of Toronto and obtained from OpenDataToronto [@opendatatoronto].
+This dataset captures the shelter use throughout the diverse urban landscape of Toronto in 2022, which is a year marked by the ongoing impacts of the COVID-19 pandemic, economic fluctuations, and changes in governmental policies affecting the homeless population.
+We analysis the data in R(@citeR), with additional tools for support the analysis, including `tidyverse`[@citetidyverse], `here`[@citehere], `dplyr`[@citedplyr], `readr`[@citereadr], `modelsummary`[@citemodelsummary], `janitor`[@citejanitor], `tibble`[@citetibble], `ggplot2`[@citeggplot2], and research method is from @tellingstorieswithdata.
 
-# Average rooms usage in Toronto Shelter of 2022
-The statistics from @tbl-torontoo and scatter plot in @fig-torontoo illustrated the mean daily occupancy rates for Toronto's shelter system in 2022, offering a detailed perspective on the impact of seasonal variations and other factors on shelter utilization.
-The occupancy rate starts at a reasonable level during the winter months and gradually increases, reaching its highest point in October at 71.5, before slightly declining towards the end of the year.
-This pattern indicates a growing demand for shelter as the year advances, especially during the autumn season.
-This increase could be linked to cooler temperatures, changes in socioeconomic conditions, or alterations in policies that impact the homeless community.
-The following abstract highlights the influence of COVID-19, the opined crisis, and increasing refugee claims on the shelter system, suggesting that these issues are major contributors to the observed changes in shelter usage.
-Although there have been efforts to make housing more accessible and provide temporary emergency shelters, the shelter system is still being challenged, as shown by the consistently high occupancy rates, especially towards the end of the year.
-This suggests that the shelter system is both adaptable and under significant strain, highlighting the urgent requirement for policymakers to modify and strengthen their assistance for the homeless population.
-This is particularly important in anticipation of future issues that could further burden the system.
+## Variables
+
+The primary factor being examined is the average number of rooms occupied daily in shelters, indicating the demand for shelter services and how it varies throughout the year of 2022.
+This analysis is further detailed by distinguishing between types of shelter programs—emergency shelters for immediate needs, and transitional shelters for longer-term stays.
+Furthermore, the study considers demographic segments such as families, men, women, mixed adults, and youth to provide insight into the diverse populations utilizing these services.
+Geographic analysis divides the data by city areas, including Etobicoke, North York, Scarborough, Toronto, and Vaughan, offering a clear view of where the demand for shelters is most pronounced within the metropolitan region.
+
+Key variables were constructed to enhance the analysis, such as categorizing months into seasons to explore potential weather-related trends in shelter usage.
+Data cleaning efforts involved addressing missing values and outliers, ensuring the reliability of the analysis.
+Details on these processes are transparently documented in our code repository.
+
+## Alternative Data Considerations
+
+While other datasets might have been available, such as individual level admission statistics or broader homelessness data.
+These were not utilized for specific reasons.
+The selected dataset's aggregate nature avoids the privacy concerns associated with individual data and provides a consistent, high-level view suitable for policy analysis.
+Additionally, the dataset's reliability and the authority of the source OpenDataToronto [@opendatatoronto] ensure a robust foundation for the investigation.
+
+## Visualizations and Summary Statistics
+To provide a better understanding in comprehension of the dataset, visualizations such as statistic (@tbl-torontoo) and scatter plots (@fig-torontoo, @fig-across_cities) have been included.
+These visuals depict monthly occupancy trends, and geographic distribution of shelter use.
 
@@
 ```
+
+The statistics from @tbl-torontoo and scatter plot in @fig-torontoo illustrated the mean daily occupancy rates for Toronto's shelter system in 2022, offering a detailed perspective on the impact of seasonal variations and other factors on shelter utilization.
+The occupancy rate starts at a reasonable level during the winter months and gradually increases, reaching its highest point in October at 71.5, before slightly declining towards the end of the year.
+This pattern indicates a growing demand for shelter as the year advances, especially during the autumn season.
+This increase could be linked to cooler temperatures, changes in socioeconomic conditions, or alterations in policies that impact the homeless community.
+
+The following abstract highlights the influence of COVID-19, the opined crisis, and increasing refugee claims on the shelter system, suggesting that these issues are major contributors to the observed changes in shelter usage.
+Although there have been efforts to make housing more accessible and provide temporary emergency shelters, the shelter system is still being challenged, as shown by the consistently high occupancy rates, especially towards the end of the year.
+This suggests that the shelter system is both adaptable and under significant strain, highlighting the urgent requirement for policymakers to modify and strengthen their assistance for the homeless population.
+This is particularly important in anticipation of future issues that could further burden the system.
 
@@
 
-# The occupancy of shelter's room in 2022 Toronto by different city, sector, and programs
-
-The first graph @fig-across_cities is a scatter plot that depicts the distribution of occupied rooms by several sectors, such as families, males, mixed adults, women, and youth, across several places, including Etobicoke, North York, Scarborough, Toronto proper, and Vaughan.
+The scatter plot (@fig-across_cities) that depicts the distribution of occupied rooms by several sectors, such as families, males, mixed adults, women, and youth, across several places, including Etobicoke, North York, Scarborough, Toronto proper, and Vaughan.
 Each dot shows the amount of rooms inhabited by a sector within a certain city.
 The most notable finding here is that Toronto has the highest occupancy rate across all categories, notably for families and mixed adults, showing a concentrated demand for shelters in the city's core.
-The second graph @fig-programs presents a stacked bar chart that compares emergency and transitional shelter occupancy in the same areas.
-Emergency shelters have substantially greater occupancy rates, particularly in Toronto, where the bar exceeds 30,000.
-This implies a strong reliance on emergency shelters, which are normally used for short-term stays, implying that there may be an immediate and pressing need for shelter that cannot be provided by longer-term solutions.
-Transitional shelters, which provide a more stable but not permanent housing alternative, have substantially lower usage, with Toronto once again leading in occupancy.
 
@@
 ```
+
+\newpage
+
+The stacked bar graph (@fig-programs) provides a detailed breakdown of room occupancy within Toronto's shelter system, comparing emergency and transitional program usage across different sectors and cities.
+The data reveals a pronounced reliance on emergency shelters, with Toronto showing the highest occupancy rates, particularly for men and mixed adults.
+In contrast, transitional shelters are utilized less, though they play a critical role for youth and women in Toronto.This difference in shelter usage indicates a urgent need for targeted policies to support sustainable housing and services.
+Such policies should aim to decrease the heavy reliance on immediate, short-term shelters and enhance the use of transitional shelters that support the progression toward stable, long-term accommodation.
+
+```{r}
+#| label: fig-programs
+#| fig-cap: "The shelter rooms usage based on different sector and services program in Toronto."
+#| echo: false
+#| warning: false
+#| message: false
+toronto_shelters_clean |>
+  drop_na(location_city) |>
+  ggplot(mapping = aes(x = location_city, fill = sector)) +
+  geom_bar() +
+  theme_linedraw() +
+  labs(x = "location_city",y = "num_occupied_rooms",fill = "sector") +
+  facet_wrap(vars(program_model), scales = "free") +
+  guides(x = guide_axis(angle = 60)) +
+  theme(legend.position = "bottom") + 
+  scale_fill_viridis_d(option = "magma")
+```
+\newpage
+
+The scatter plot(@fig-models) illustrates the relationship between the occupancy rate of rooms and the actual room capacity in Toronto's shelters.
+Each point represents a data pairing of these two variables, showing a positive trend: as the occupancy rate increases, the actual capacity used also tends to increase.
+The red line indicates the average trend, cutting through the data to demonstrate the general direction of this relationship.
+This graph indicats that as more people use the shelters, the actual number of rooms occupied goes up, which could strain the shelter system.
+The analysis underscores the importance of using predictive models to inform policy decisions and resource allocation, ensuring that the shelter system can accommodate the needs of Toronto's homeless population effectively.
 
@@
 
+\appendix
+
+# Appendix {-}
+
+# Model details {#sec-model-details}
+
+## Posterior predictive check
+
+we implement a posterior predictive check. This shows...
+we compare the posterior with the prior. This shows...
+
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-ppcheckandposteriorvsprior
+#| layout-ncol: 2
+#| fig-cap: "Examining how the model fits, and is affected by, the data"
+
+pp_check(toronto_shelters_data_first_model_rstanarm) +
+  theme_classic() +
+  theme(legend.position = "bottom")
+```
+
+## Diagnostics
+
+is a trace plot. It shows... This suggests...
+
+is a Rhat plot. It shows... This suggests...
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-stanareyouokay
+#| fig-cap: "Checking the convergence of the MCMC algorithm"
+#| fig-subcap: ["Trace plot", "Rhat plot"]
+#| layout-ncol: 2
+
+plot(toronto_shelters_data_first_model_rstanarm, "trace")
+
+plot(toronto_shelters_data_first_model_rstanarm, "rhat")
+```
+
+\newpage
 # References

### 2024-03-17 paper/datasheet_template.qmd
Final verison

@@
 thanks: "Code and data are available at: https://github.com/Sinanma/shelter_in_Toronto"
-date: "`r Sys.time()`"
-date-format: "12 March, 2024"
+date: today
+date-format: long
 abstract: "The study examines the impact of the COVID-19 pandemic and government policies on Toronto's shelter system in 2022.

### 2024-03-17 paper/paper.qmd
Final verison

@@
 thanks: "Code and data are available at: https://github.com/Sinanma/shelter_in_Toronto."
-date: 12 March, 2024
+date: today
 date-format: long
